\textsf{Are large language models superhuman chemists?}

### 2024-03-24 src/tex/ms.tex
Update ms.tex

    However, we still have only very limited systematic understanding of the chemical reasoning capabilities of LLMs, which would be required to improve models and mitigate potential harms. 
    Here, we introduce \enquote{\chembench,} an automated framework designed to rigorously evaluate the chemical knowledge and reasoning abilities of state-of-the-art LLMs, including GPT-4, against the expertise of human chemists.

@@

Yet, given that the models outperform the average human in our study, it is clear that we need to rethink the way we teach and examine chemistry.
Critical reasoning is increasingly important and rote solving of problems or memorization of facts is clearly a domain in which \glspl{llm} will continue to outperform humans.

>>>>

    However, we still have only very limited systematic understanding of the chemical reasoning capabilities of LLMs, which would be required to improve models and mitigate potential harms. 
    Here, we introduce \enquote{\chembench}, an automated framework designed to rigorously evaluate the chemical knowledge and reasoning abilities of state-of-the-art LLMs against the expertise of human chemists.

@@

Yet, given that the models outperform the average human in our study, it is clear that we need to rethink the way we teach and examine chemistry.
Critical reasoning is increasingly important and robotic solving of problems or memorization of facts is clearly a domain in which \glspl{llm} will continue to outperform humans.
